\section{Beef Stew}
\begin{recipe}

\pre {
    You want to fully develop flavor, but also have some texture to 
    the beef, potatoes, and a carrots. This recipe takes 3\sfrac{1}{2} hours, 
    but can also be started well ahead of that.
}

\ingredients{
    2 & lbs stew beef \\
    \sfrac{1}{4} & cup flour \\ 
    2 & bay leaves \\
    & kosher salt \\
    & pepper \\
}

Combine flour, pepper and salt in a bowl. Cut beef into two inch pieces and toss to coat. 

\ingredients{
    & vegetable oil \\
}

Brown beef in a dutch oven with vegetable oil. Don't crowd the pan. 
Work in three or four batches, five minutes per side. Remove beef to a plate. 

\ingredients{
    1 & large onion \\
    & kosher salt \\
}

Chop onions. Add onions and salt. As the onions cook, scrape up the fond on the bottom 
of the pan. 

\ingredients{
    4 & cups beef broth \\
    1 & cup red wine \\
    2 & tablespoons cider vinegar \\
}

Add liquid ingredients to the pot, and reintroduce the beef. 
Simmer on low for 90 minutes, skimming the surface residue, occasionally. 

At this point, you can let the stew cool and finish it 90 minutes before dinner. 

\ingredients{
    3 & large carrots \\
    1 & large russet potato \\
}

Peel and cut carrots into rounds. Peel and slice the potato into \sfrac{1}{2} inch cubes. 
Add to stew. Finish in the oven at 350\degree{} for 1 hour.

Let cool for 30 minutes. Season to taste with salt, pepper, and cider vinegar. 

Serve with a baguette or egg noodles.

\end{recipe}
