\section{Horseradish-Crusted Beef Tenderloin}
\begin{recipe}

\pre{
    The gelatin is the key to getting the crust to stick, even when you slice it. A 2.5 pound roast is 
    good for 4 adults and 2 children. Ask for a center-cut Chateaubriand fillet roast. Use jarred horseradish. 
}

\ingredients{
    2.5 & pound beef tenderloin \\
}

If the butcher did not do it, trim excess fat and remove silver skin. 

Sprinkle liberally with kosher salt, and rest in the refrigerator for 24 hours. Remove from refrigerator
and bring to room temperature for 1 hour. 

Pre-heat oven to 400\degree{}.

\ingredients{
    3 & tablespoons Panko breadcrumbs \\
    1 & tablespoon vegatable oil \\
}

Toast breadcrumbs over medium high heat, and remove to a medium sized bowl.

\ingredients{
    1 & shallot \\
    2 & cloves garlic \\
    2 & tablespoons minced parsley \\ 
    1 & tablespoon minced thyme \\ 
    2 & tablespoons horseradish \\    
    1 & russet potato \\
    1 & cup vegetable oil \\
}

Mince shallot and garlic. Combine with herbs. Pat horseradish dry with a paper towel, and combine. Peel 
potato, and grate on a box grater. Shallow fry potato over medium high heat until well browned. Strain oil, 
and let cool. Put potato into a ziploc bag and crush. Combine with breadcrumb mixture. 

Pat tenderloin dry, and season with pepper. Brown all four sides in a large dutch oven, or a frying pan. 
Let rest for 10 minutes before coating. 

\ingredients{
    1 & tablespoon mayonnaise \\
    1 & tablespoon dijon mustard \\
    2 & tablespoons horseradish \\
    \sfrac{1}{2} teaspoons powdered gelatin \\
}

Combine mayonnaise, mustard, and horseradish. Right before coating the beef, stir in gelatin. Coat beef on three 
sides using a brush. Roll in the breadcrumb mixture, pressing down so that it adheres. 

Roast on a wired rack on a baking sheet for 30 minutes, or until 135\degree{} for medium. Roast will climb another
10\degree{} while it's resting. Rest for at least 20 minutes before serving. Slice into fillets. 

\tip {
    A good sauce to serve with is another jar of horseradish, enough heavy cream to loosen, and 
    salt and pepper to taste. 
}

\end{recipe}
