\section{Thai Cashew Chicken (Gai Pad Med Ma Muang)}
\begin{recipe}

\pre{    
    Serve with Jasmine rice.
}

\ingredients{
    1 & tablespoon soy sauce \\
    2 & tablespoons flour \\
    1\sfrac{1}{2} & lbs chicken thighs \\ 
      & salt \\
      & pepper \\
}

Combine soy sauce and flour with a whisk. Slice chicken to \sfrac{3}{4} inch cubes and 
toss in sauce. 

Put a wok or cast iron pan over high heat. Don't preheat for more than a few minutes 
or the first oil could burn. 

\ingredients{
    5 & tablespoons vegetable oil \\
}

Stir fry each batch staring with 1 tablespoon of oil. 

Stir fry chicken in two batches. Remove to temporary bowl. 

\ingredients{
    1 & cup roasted cashews \\
}

Stir fry cashews. Remove to bowl. 

\ingredients{
    5 & Arbol chiles \\
    1 & teaspoon red pepper flakes \\
    6 & garlic cloves \\
}

Press garlic into a mince and combine ingredients into a small bowl. 

\ingredients{
    1 & red onion \\
}

Slice onion into one inch chunks. 

Stir fry garlic, red pepper. Add onions. Cook for 2 minutes. 

\ingredients{
    2 & tablespoons soy sauce \\
    1\sfrac{1}{2} & tablespoons Thai Kitchen roasted red chili paste \\
    1\sfrac{1}{2} & tablespoons sugar \\
    1 & tablespoon oyster sauce \\
    3 & tablespoons water \\
}

Whisk in a bowl. 

Add chicken back to pan. Add roasted red pepper sauce. Cook for 2 minutes. 

\ingredients{
    1 & bunch scallions \\
}

Slice green onions into one inch pieces and add to pan. Cook for 1 minute.

\end{recipe}
