\section{Julie's Cinnamon Rolls}
\begin{recipe}

\pre{
    Makes about 16 rolls. 
    You can substitude coconut oil for shortening. 
    You can make these the night before, just cover airtight. 
}

\ingredients{
    2 & cups milk \\
    16 & tablespoons butter \\ 
    1 & tablespoon shortening \\
    \sfrac{3}{4} & cup sugar \\
}

Combine and bring to 185\degree{} over medium heat.

\ingredients{
    \sfrac{1}{2} & cup warm water \\
    3 & tablespoons yeast (3 packets) \\ 
    2 & tablespoons sugar \\
}

Combine and let rise until doubled in size in a medium-large bowl for 30 minutes.

\ingredients{
    6\sfrac{1}{2} & cups flour \\
    2 & teaspoons kosher salt \\
    3 & eggs \\     
}

Whisk flour and salt. Add milk mixture. The flour will cool it down enough 
to not kill the yeast. Stir in beaten eggs and the yeast. 

Put into a buttered bowl and place in a proofing oven until doubled in size, 
60 minutes. 

Separate into two halves. Knead lightly until smooth. 
Roll each into a rectangle on a floured surface. 

\ingredients{
    8 & tablespoons butter \\
    \sfrac{1}{4} & cup sugar \\
    1 & teaspoon cinnamon \\
}

Combine softened butter with sugar and cinnamon.
Smear half of the butter on the dough, and reserve half. 

Roll dough and cut into 1\sfrac{1}{2} inch rounds. 

At this point, you have the option of holding the rolls overnight 
and baking in the morning.

Arrange in a 12x9 baking pan. The rolls with merge together, leave some space. 
Let rise in a warm location for 30 minutes. 
Bake for 15 minutes at 350\degree{} until just light brown. 
You want them to look under-baked.

\ingredients{
    8 & tablespoons butter \\
    6 & tablespoons sour cream \\
    2 & teaspoons vanilla \\
    2 & cups powdered sugar \\
}

Combine frosting and spread over cooled rolls. 

\end{recipe}
