
\section{Cream of Mushroom and Chicken}
\begin{recipe}

\pre{
    This is great for a cold week night, and it re-heats very well.
    Shredding the chicken versus cutting into pieces helps the texture.
}

\ingredients{
    2 & bone-in chicken breasts, skin on \\
}

Roast in a pan in the oven at 450 degrees for 20 minutes. Cool, discard skin and bones and slice into chunks.

\ingredients{
    10 & ounces dried shittake mushrooms\\
     1 & package fresh button mushrooms \\
     3 & cloves garlic \\
     2 & tablespoons olive oil \\
}

Rehydrate fried mushrooms in water for 15 minutes.
Sauté all mushrooms in oil over medium heat for 10 minutes, and then add minced garlic.

\ingredients{
    1 & cup heavy cream \\
    1 & cup half and half \\
}

Combine in a dutch oven along with mushrooms, and return to medium heat.

Simmer for 10 minutes. The goal is not to evaporate all the liquid.

Blend using a standing blender (not a stick blender) until very smooth.

\ingredients{
    1 & package frozen peas \\
    1 & red pepper \\
}

Shred chicken into small pieces and add to soup mixture, along with peppers and peas. Season to taste with salt and pepper. If it needs acid, you can add white wine.

\ingredients{
    1 & cup rice \\
    1 & package puff pastry \\
}

Start the rice, and follow package instructions to bake puff pastry. Most pastry needs to be brought to room temperature for 40 minutes. It's easy to underbake the pastry; leave it in longer.

Serve inside a puff pastry on top of rice.

\end{recipe}
