
\section{Ham and Scalloped Potatoes}
\begin{recipe}

\pre{
    The scalloped potatoes can be prepped ahead of time, even the day before. Simply pause at the step when they go into the oven, and refrigerate instead.
}

\subsection{Ham}

\tip {
    Many recipes suggest that 10-15 minutes per pound is sufficient.
    You can't really over-cook a ham. I prefer to cook for 20 minutes a pound which develops a better crust anyway.
    Make sure to trim any inedible skin off the ham first. If at all possible, try not to get a ham with water added, it's hard to fix that texture.
}

\ingredients{
    1 & large ham, bone in \\
    3 & apples \\
    2 & onions \\
    1 & cup water \\
    1 & cup brown sugar \\
}

Quarter apples and onions and place in the bottom of a roasting pan along with the water.

Score the surface of the ham with a cross hatch pattern at once inch intervals.

Place ham on a rack in the roasting pan. With your hands, pack brown sugar on to the sides of the ham.

Roast in the oven at 350\degree{} for 20 minutes per pound.

\ingredients{
    1 & cup apple jelly \\
}

With 90 minutes remaining on the roast time, remove ham from oven and brush with the jelly. Return to oven.

After the ham has rested, take the largest section off the bone and slice thinly.

\subsection{Gastrique Sauce}

\ingredients{
    \sfrac{1}{3} & cup cider vinegar \\
}

Remove ham from oven, and remove rack from the roasting pan. Set aside and tent loosely for foil for at least 30 minutes.

To make the sauce, remove solids from the roasting pan surface, and add cider vinegar. Simmer lightly on the stove top, until reduced to taste. You can also season with salt and pepper.

When the sauce is reduced to a good volume and has good flavor, reduce heat to low or just turn the stove off and let the pan keep the sauce warm.

Pass the sauce at the table, separately from the ham.

\subsection{Scalloped Potatoes}

\tip{
    I like a strong garlic flavor in these which is non-traditional. You can make these in a regular dutch oven, but if you have an over-sized dutch oven, that will pre-cook the potatoes more evenly.
}

\ingredients{
    2 & tablespoons butter \\
    1 & large onion \\
    4 & cups heavy cream \\
    5 & garlic cloves \\
    2 & bay leaves \\
      & fresh thyme \\
      & kosher salt \\
}

Mince onion and sauté in butter with salt. Add cream, and bring to simmer. Add minced garlic and bay leaves. Tie thyme sprigs into a bunch and steep in the cream.

\ingredients {
    5 & pounds russet potatoes
}

Peel potatoes, and slice to \sfrac{1}{8} inch. This is best done on a mandolin. Combine potatoes and cream, place in a large Pyrex dish, put in the oven on 400 for 40 minutes, until they feel soft when poked with a pairing knife.


\ingredients {
    8 & ounces Gruyere cheese \\
    8 & ounces Fontina cheese \\
}

Top potatoes with shredded cheese, and bake for 20 minutes. Broil briefly for color.

\end{recipe}
