
\section{Lasagna}
\begin{recipe}

\ingredients{
               4 & tablespoons butter \\
    \sfrac{1}{4} & cup flour \\
               4 & cups whole milk \\
               1 & teaspoon kosher salt \\
               8 & ounces Parmesan cheese  \\
}

To create the bechamel sauce, melt butter in a sauce pan. Add flour and whisk. Cook for two minutes, stirring frequently. Slowly whisk in milk. Add salt. Increase heat to medium high and simmer for 10 minutes, stirring occasionally. Melt in Parmesan.

\ingredients{
    15 & ounces ricotta \\
     1 & cup fresh basil \\
     1 & egg \\
       & fresh pepper \\
}

Combine all items in a bowl.

\ingredients{
     1 & box no-bake Lasagna noodles \\
    15 & ounces mozzarella \\
     1 & box no-bake Lasagna noodles \\
       & tomato or ragu sauce; see bellow recipe \\
}

Combine tomato sauce and bechamel. Pour a large ladle of sauce in the bottom of a 9x13 baking dish, and spread it out.

Lay down a layer of noodles, followed by a layer of the ricotta mixture, a layer of sauce and a layer of grated mozzarella.

Repeat with a second layer.

\ingredients{
    10 & ounces Gruyere cheese \\
     1 & tablespoons garlic powder \\
}

Top with a final layer of noodles, and the grated Gruyere.

Cover with tin foil, and bake at 375\degree for 15 minutes. Remove foil, and bake another 25 minutes.

Remove from the oven, and let cool for 10 minutes before serving.

\subsection{Meat Sauce}

\pre{
    Meatloaf mix is sold as such in most grocery stores; it's a mix of beef, veal and pork. You can also substitute 80 percent beef.
}

\ingredients{
    28 & ounces diced tomatoes \\
    28 & ounces tomato puree \\
     1 &  pound meatloaf mix \\
     5 &  cloves garlic \\
     1 &  tablespoon tomato paste \\
     1 &  tablespoon red pepper flakes \\
     1 &  large onion \\
}

Chop onion fine, and sauté in oil until just starting to brown. Stir in tomato paste, red pepper flakes and minced garlic, for 30 seconds. Stir in meat, breaking into small pieces.

When the meat just starts to loose its color, stir in tomatoes and simmer uncovered for at least 20 minutes, or up to 3 hours. The longer, the better.

\subsection{Homemade Ricotta}

\ingredients{
               1 & gallon milk \\
    \sfrac{3}{4} & cups lemons juice(6 lemons) \\
               2 & teaspoons kosher salt \\
}

Bring milk and salt to 185\degree in a large stock pot. Remove from heat, and stir in lemon juice. Allow to rest for 20 minutes.

Pour mixture through a cloth stretched over a colander, and let drain for an hour. Cover with plastic wrap, and refrigerate for between 10 and 24 hours.

If the milk does not separate into curds and whey within 5 minutes of adding the lemon juice, add a couple more tablespoons and wait another 5 minutes. You can substitute plain white vinegar for some of the lemon juice, if you run short.

\subsection{Garlic Bread}

\pre{
    This recipes coats the bread after it comes out of the oven. Most garlic bread recipes coat the bread before it goes into the oven, which leads to soggy bread.
}

\ingredients{
    8 & garlic cloves \\
    1 & tablespoon veg oil \\
}

Mince garlic, combine with oil in a small bowl a microwave on low for up to a minute. The garlic should mellow and loose some of its raw taste.

\ingredients{
               5 & tablespoons butter (room temperature) \\
    \sfrac{1}{4} & cup fresh parsley \\
}

Combine garlic, butter and parsley in a small bowl.

\ingredients {
    1 & loaf French bread \\
}

Cut the bottom off the loaf, and then halve the loaf lengthwise. Place on a baking sheet in a 450\degree oven for 10 minutes, or until well browned.

\ingredients {
    \sfrac{1}{2} & cup finely grated Parmesan \\
}

Remove bread from the oven, slather with garlic butter mixture, top with Parmesan and wrap tightly in aluminum foil.
After 5 minutes, bread can be sliced while still inside foil and served.

\end{recipe}
