
\section{Fleming's Macaroni and Cheese}
\begin{recipe}

\pre{
    This is the actual recipe for a favorite side-dish from Fleming's Steak House. The recipe was published on the web by their head chef.

    Finding smoked cheddar can be somewhat challenging, but it is critical to the dish.
}

\ingredients{
    1 & box cavatappi pasta \\
    2 & teaspoons salt \\
    1 & tablespoon veg oil \\
}

Bring one gallon of water to boil. Add 2 teaspoons salt and cook pasta very al-dente. Drain pasta and cool under cold running water. Toss drained pasta in oil and reserve.

\ingredients{
    \sfrac{3}{4} & cup onion, small dice \\
               1 & stick unsalted butter \\
               3 & tablespoon flour \\
}

In a dutch oven, sauté onions over medium heat. Add flour and cook for one minute, but do not brown.

\ingredients{
    2 & cups heavy cream  \\
    3 & cups half and half \\
    2 & teaspoons kosher salt \\
    1 & teaspoon white pepper \\
}

Add cream, half and half, kosher salt and white pepper. Bring pot to a simmer. Cook until sauce is thick, about 5-6 minutes.

\ingredients{
    \sfrac{3}{4} & pound smoked cheddar \\
    \sfrac{1}{4} & pound cheddar cheese \\
}

Still in the dutch oven, blend grated cheese into sauce until melted. Add pasta.

\ingredients{
               1 & tablespoon veg oil \\
               1 & teaspoon chipotle powder \\
    \sfrac{3}{4} & cup panko bread crumbs \\
}

Sauté oil and chipotle powder over medium-high heat for 30 seconds. Remove from stove and stir in bread crumbs.

Sprinkle bread crumbs over the pasta and bake for 15-20 minutes at 350\degree.

Variation: add chunks of roasted broccoli.

\end{recipe}
