\section{Broccoli Sausage Orecchiette}
\begin{recipe}

\pre{
    This recipe relies on a good parmesan cheese, and a good olive oil. Don't
    skimp on the full half cup of oil. The other key is to break the broccoli and 
    sausage down into small pieces, so that they fit into the orecchiette. 
}

\ingredients{
               1 & package sausage roll \\
    \sfrac{1}{2} & cup olive oil \\
               1 & tablespoon red pepper flake \\
}

Pre-heat oven to 550\degree{}.

Shallow fry sausage roll and red pepper flakes in olive oil in a dutch oven over medium-high heat until
browned. Removed with a slotted spoon and process in a food processor for 3
short bursts. This will break up the sausage into the right sized pieces.
Return to pan and brown for another 10 minutes on medium heat. You may need to add a
little more oil so that all of the sausage browns evenly. 

Drain sausage, reserving the oil.

\ingredients{
    2 & heads broccoli \\
      & salt \\
      & pepper \\
}

Dice broccoli stalk and florets into small pieces that can fit into the pasta. 

Toss in the reserved sausage oil in the now empty dutch oven. Season with salt and papper. 
Turn out into a foiled baking sheet, and place under the broiler until lightly blackened.

\ingredients{
    1 & box Orecchiette pasta \\
}

Boil paste until al dente, as per box instructions. Drain, reserving a bowl
of the water.

Add the sausage and broccoli to the pasta. Toss to combine.
Season with salt to taste. 

\ingredients{
    3 & ounces parmesan \\
}

Grate the parmesan on a microplane. When the pasta has cooled for 3
minutes, toss with cheese and reserved pasta liquid. The goal is to create a
cheese sauce.

\tip {
    Great with Sriracha.
}

\end{recipe}
