\section{Quick Pizza}
\begin{recipe}

\pre{
    Many supermarkets sell pre-made pizza dough. This dough can be frozen, even
    if it is fresh in the supermarket. Defrost by moving to the refrigerator
    ONE day in advance.
}

\ingredients{
    1 & pizza dough \\
}

Turn into a bowl well-coated with olive oil, cover in plastic wrap, and let
come to room temperature for two hours. If you don't have time for that, you
can put it in a plastic bag w/ olive oil, remove as much air as possible, and
submerge in warm water for 30 minutes.

Cut a large square of parchment paper, and empty pizza dough onto it. Lift the
edges with your hands and stretch it out a little. Then use the palms of your
hands to spread it further. Don't spread it too thin; you want some chew in
the final crust.

\ingredients{
      15 & ounces crush tomato (ideally San Marzano) \\
      1 & teaspoon oregano \\
      2 & garlic cloves \\
}

Just blend it with an immersion blender, right in the can. It will make enough
for 3-4 small pizzas. You can also use fresh tomatoes, but then you should saute it in a pan to reduce.

\ingredients{
     6 & ounces shredded mozzarella \\
     2 & ounces shredded Parmesan \\
     6 & ounces pepperoni \\
}

Cover dough with sauce, cheese and pepperoni. There is no such thing as too much
pepperoni.

You should be able to cook the pizza in just 10 minutes.
The faster you can cook it, the better the pizza will be.

Remove from oven and cool on wired rack.

\subsection{Pizza Dough}

\ingredients{
      2 & cup warm water \\
      1 & packet instant yeast \\
      4 & tablespoons olive oil \\
      3 & cups bread flour \\
      2 & tablespoons kosher salt \\
}

Manually mix everything except the water in a large, air tight container. Add water until it's too wet, then add in a little more flour - mixing well. When it's loose and sticky but not a puddle put the lid on the container and let it rest at room temperature for 3-4 hours. Then put in the fridge.

Dough is best if you let it ferment in the fridge for 3-4 days.

\end{recipe}
