\section{Premium Pork Ramen}
\begin{recipe}

\tip {
    Home made chicken stock is best.
}

\ingredients{
     & small pork shoulder \\
      & salt
}

Halve the pork shoulder. Salt one half for 24 hours, and roast in a 325\degree
oven for 5-6 hours, or until a fork falls through the meat. Allow to cool
to room temperature and set aside.

\ingredients{
      & remaining pork shoulder \\
}

Slice into one inch cubes, and place in the freezer for 15 minutes. Process in
the food processor until it's the texture of pancetta.

\ingredients{
    & vegetable oil \\
  1 & onion \\
  6 & garlic cloves \\
  1 & inch of ginger \\
}

Heat oil in a dutch oven over medium heat. Add chopped pork and sauté until
well browned. Dice onion, smash garlic and grate ginger. Add all ingredients
to the dutch oven and soften for 3 minutes.

\ingredients {
    8 & cups chicken stock \\
}

Deglaze dutch oven with chicken stock. Bring to simmer, reduce to low and
simmer for 40 minutes.

Pour broth through a fine mesh strainer into a container. Reserve.

\ingredients {
    4 & ramen packets \\
}

Discard flavor packets. Boil noodles for just 2 minutes. Drain noodles and
place directly into serving bowls.

Return broth to dutch oven. Bring to simmer.

\ingredients {
    & miso paste \\
    & fermented red pepper paste \\
}

Whisk half a cup of the broth into the pastes to combine. Stir mixture back
into the broth.

\ingredients {
    2 & tablespoons soy sauce \\
    1 & tablespoon mirin \\
      & sesame oil \\
    4 & scallions \\
      & sesame seeds \\
}

Add wet ingredients to the pot. Slice roasted pork thinly, and add directly to
the serving bowls, on top of the noodles. Pour broth over the noodles, and
let sit for 3 minutes to warm. Add sliced scallions and sesame seeds and serve.

\end{recipe}
