\section{Chicken Pot Pie}
\begin{recipe}

\tip {
    You can either use a rotisserie chicken, or chicken breasts that you
    bake or boil. Shredded chicken is better in the dish than chopped. 
}

\ingredients{
     \sfrac{1}{2} & cup sour cream \\
                1 & egg \\ 
    2\sfrac{1}{2} & cups flour \\
    1\sfrac{1}{2} & teaspoons salt \\
               12 & tablespoons butter \\
}

Beat eggs with sour cream. Process dry ingredients in a food processor, and
add butter in pieces. Slowly add egg mixture. Stop when dough just begins to
form. Transfer to a floured surface and kneed. Divide into two halves, and form
into discs. Wrap in plastic and put into the refrigerator for at least one hour.

Remove dough from plastic, and roll one into a 12 inch circle. Transfer to the 
bottom of a 9 inch pie dish. Press dough into the edges. Wrap in plastic, and put
the dish into the refrigerator for at least 30 minutes. 

Roll the other half of the dough, cover in plastic, and move to the refrigerator
on a separate plate. 

\ingredients{
                4 & tablespoons butter \\ 
                1 & onion \\ 
                2 & carrots \\ 
                2 & celery ribs \\
                6 & tablespoons flour \\
    2\sfrac{1}{2} & cups chicken broth \\
     \sfrac{1}{2} & cup half and half \\
                1 & russet potato \\
                1 & teaspoon minced fresh thyme \\
    2\sfrac{1}{2} & lbs chicken \\
                1 & cup frozen peas \\
}

Start the oven at 450\degree. Poach chicken in shallow water for 15 minutes, 
then cool and shred. 

Melt button in a dutch oven on the stove top, on medium heat. Add onions, 
carrots, and celery. Season with salt and pepper. Cook for 5 minutes. Add
flour, and cook for another 2 minutes. Add chicken broth, and half and half. 

Add potato and thyme. Reduce heat and simmer for 8 minutes. 

Turn off the heat, and add chicken and peas. 

Assemble pie. Trim upper crust as needed, and pinch the seams together using 
your fingers. Cut four slots in the top of the crust. Brush with egg wash.

Bake at 450\degree for 20 minutes. Reduce oven to 375\degree and bake for 
another 15 minutes. 

Let pie cool for 45 minutes. 

\end{recipe}
