\section{Potato Salad}
\begin{recipe}

\pre{
    The key to this potato salad is cooking and cooling the potatoes completely, before 
    cutting them up, or stirring them. Otherwise, the potatoes start to break down and 
    muddy the salad. While they are hot, you want to both salt and season them with 
    vinegar (pickle juice). If you can cook the potatoes inside a fitted colander inside 
    a large pot, then they will bairly be distrubuted while cooking or cooling. 
}

\ingredients{
    5 & pounds medium or small yukon gold potatoes \\
    4 & quarts water \\
    & kosher salt \\    
    & pickle juice \\ 
}

Slice potatoes into one inch chucks. 
Heavily salt water, put potatoes in, and bring to a boil. The water does not need to 
be at a boil before you put the potatoes in. Once boiling, reduce heat to a 
medium boil. Cook for 15 to 25 minutes, or until a knife easily pierces a potato. 

Drain potatoes using a colander. Place a colander with potatoes inside a large bowl. 
Pour (strained) pickle juice over the hot potatoes. Using another large bowl, move 
colander back and forth, and continue to pour the pickle juice over the potatoes every 
minute, until they stop steaming.

Leave potatoes out at room temperature to cool completely, before cutting them. 

\ingredients{
                2 & cups mayonnaise \\
                3 & celery stalks \\
                1 & small white onion \\
                1 & handful fresh dill \\
                1 & handful fresh parsley \\
                1 & tablespoon celery seed \\
                2 & tablespoons dijon mustard \\
}

Slice celery and onion and add to potatoes. Mince dill and parsley. 
Whisk herbs and web ingredients. Season to taste with salt and pepper.

\ingredients{
      & paprika \\
      & frozen peas \\ 
}

Combine the potatoes and sauce, and top with paprika and defrosted peas.

\end{recipe}
