\section{Roast Chicken and Green Beans}
\begin{recipe}

\pre{
    This is one of Noel's favorite weeknight meals.
    The baking powder helps the skin get crisp. 
}

\ingredients{
    1 & 4-5 pound chicken \\
      & kosher salt \\
      & baking powder \\
}

Using a pairing knife, create openings in the skin near the breast and the drumsticks. Get under the skin with the handle of a metal spoon, and create separation. This will help develop a crisper skin.

Using your hands, spread a generous amount of salt and the baking powder on top of the skin, under the skin, and inside the main cavity. This will help keep the meat moist under high heat.

Tent loosely with paper towels and place in the fridge over night.

The next day, preheat the over to 450 with the empty pan in it. 

\ingredients{
      & melted butter \\
}

Place the chicken in the hot pan, and brush with melted butter. 

Cook for 35 minutes, or until the chicken is 120. 

Turn off the over, and let the chicken coast until 165. 

\ingredients{
      1 & pound green beans, ends removed \\
      1 & shallot \\
      1 & lemon \\
        & kosher salt \\
        & butter \\
}

When the chicken is done, remove pan from oven and place the chicken on a wire rack to rest.

Slice shallot and sauté in the hot pan with some salt. Use the moisture from the shallots to loosen the bits of fond in the pan.

Add a pad of butter, the green beans, and more salt. Cook over medium high heat for 10 minutes. Add lemon juice and stir to combine.

Slice chicken and serve.

\end{recipe}
