
\section{Taco Night}
\begin{recipe}

\pre{
    Ideally, left over pot roast or puled pork would be substituted for the ground beef.

    With ground beef, you want to nearly burn it to develop some flavor.
}

\ingredients{
    1 & pound ground beef (90%) \\
}

Fry in a cast iron pan over medium-high heat. Don't flip it at all for at least 10 minutes.

\ingredients{
               2 & tablespoons chili powder \\
               1 & teaspoon cumin  \\
               1 & teaspoon coriander  \\
    \sfrac{1}{2} & teaspoon oregano  \\
    \sfrac{1}{4} & teaspoon cayenne \\
    \sfrac{1}{4} & cup chicken broth \\
               1 & can Adobe sauce, chilies removed \\
}

Dump the spice mixture on top. Smother in chicken broth and Adobe sauce, and stir to combine.

Cook for 10 minutes. Turn out into a paper towel lined bowl.

\ingredients{
    8 & six inch corn tortillas \\
    2 & cups vegetable oil \\
}

Heat the vegetable oil over medium heat in a frying pan just big enough to fit one tortilla.

When the oil shimmers, place a single tortilla in the pan, and let it fry for 30 seconds.

Using long handled tongs, grip one side of the tortilla, and fold it over at a 60 degree angle, holding it there for another 30 seconds.

Flip and fry the first side for another 30 seconds. Remove to a paper towel lined cooling rack.

\ingredientsLeft{
    & sour cream \\
    & Monterrey jack cheese \\
    & onion \\
    & refried beans \\
    & lettuce \\
    & lime wedges \\
    & yellow rice \\
}

Serve with various accouterments.

\tip{
    You can substitute packaged taco seasoning for the spice mixture, but don't skip the Adobo.

    Try wrapping the fried taco in a flour tortilla. It provides a safety margin for too-crisp corn tortillas.
}

\end{recipe}
