\section{Bean and Cheese Tomatillo Enchiladas}
\begin{recipe}

\ingredients{
    2 & lbs fresh tomatillos \\
      & olive oil \\
      & kosher salt \\
}

Unwrap tomatillos, halve and toss with olive oil and kosher salt. Spread on a
baking sheet, face down, and broil for 10 minutes until blackened. Remove, let
cool and pulse in a food processor.

\ingredients{
    1 & onion \\
    2 & cans pinto beans \\
    3 & garlic cloves \\
    2 & jalapeños \\
      & vegetable oil \\
      & chicken stock \\
}

Sauté minced onion in vegetable oil until just browned. Add sliced jalapeños,
pinto beans with the can liquid and smashed garlic cloves. Add chicken stock to come up to
half way as high as the beans, and simmer for 15 minutes. Smash beans with a
potato masher, leaving some bean texture.

\ingredients{
    1 & lbs Monterey jack cheese \\
    1 & bunch cilantro \\
}

Shred cheese and mix with minced cilantro, stems included.

\ingredients{
    8 & large flour tortillas \\
}

Warm the tortillas in a microwave and char individually over an open gas flame.

Spread one cup of the tomatillo sauce on the bottom of a large casserole dish.
Roll each tortilla around a generous amount of beans and cheese filling, and
place in the dish seam side down.

Cover with remaining tomatillo sauce, and make sure there is no dry tortilla.

Bake for 20 minutes at 350\degree until cheese is just melted.

\ingredients{
    & radishes \\
    & sour cream \\
    & hot sauce \\
}

Serve with accoutrements.

\end{recipe}
