
\section{Vermicelli Bowl}
\begin{recipe}

\pre {
    There is no broth in this recipe, just a bunch of toppings and the noodles.
}

\ingredients{
    2 & carrots \\
    2 & cups white vinegar \\
}

Create a simple pickle by slicing carrots into thin sticks and pouring boiling vinegar over. Let sit for one hour and drain.

\ingredients{
    8 & scallions \\
    1 & cup simple sugar \\
}

Simple sugar is equal parts sugar and water, boiled and cooled. Slice scallions and add to cooling syrup.

\ingredients{
            1 & cucumber \\
            1 & package bean sprouts \\
            1 & bunch mint \\
            1 & bunch cilantro \\
 \sfrac{1}{2} & cup peanuts \\
            1 & tablespoon sesame seeds \\
            3 & jalapeños \\
}

Slice cucumber, mint, and jalapeños thinly. Cilantro leaves should removed from stalks. Peanuts should be chopped finely.

\ingredients{
    1 & pound rice noodles \\
}

Either buy pre-cooked noodles, or cook, rinse and chill the noodles yourself.

Combine noodles, veggies and toppings in each serving bowl.

\ingredients{
    & fish sauce \\
    & Sriracha \\
    & lime wedges \\
}

Top with fish sauce, Sriracha and lime to taste. I think a quarter cup of good fish sauce straight is fine. If you like something milder, you can water down the fish sauce with either water or sugar and lime juice.

\tip{
    You can also top with small amounts of protein. Crispy fried pork is a good pairing. Other potential additions are Romain lettuce, shallots and Thai basil.
}

\end{recipe}
