\section{Fluffy Yellow Cake}
\begin{recipe}

\pre{
    Bring ingredients to room temperature ahead of time, including the buttermilk. 
}

Set oven to 350\degree{}. 
Line the bottoms of two 9-inch pans with parchment paper. 
Grease pans with cooking spray and dust with flour. 

\ingredients{
    2\sfrac{1}{2}  & cups cake flour \\ 
    1\sfrac{1}{4} & teaspoons baking powder \\
    \sfrac{1}{4}  & teaspoons baking soda \\
    1\sfrac{1}{2} & cups sugar \\ 
}

Whisk ingredients in a large bowl. 

\ingredients{
    10 & tablespoons butter \\
    1  & cup buttermilk \\
    3  & tablespoons vegatable oil \\
    2  & teaspoons vanilla extract \\
    6  & egg yolks \\
}

Melt butter. Reserve egg whites. Whisk wet ingredients in a small bowl. 

\ingredients{
    \sfrac{1}{4} & cup sugar \\
}

In a stand mixer with a whisk attachment, beat egg whites until foamy. 
Add sugar and beat to stiff peaks. Set aside, emptying the mixing bowl.

Put the flour mixture into the mixing bowl and set speed to low.
Slowly add wet mixture to combine. Stop mixer and scrape the bowl.
Return mixer to medium-low and beat until smooth. 

Using a spatula, stir \sfrac{1}{3} of whites into batter. Then fold in remaining whites.

Divide batter evenly between the two cake pans, tapping pans on the counter a few times. 

Bake for about 20 minutes. Cool for 10 minutes and flip cakes onto a wire rack.

\ingredients{
    20 & tablespoons unsalted butter \\
    1 & cup confenction sugar \\
    \sfrac{3}{4} & cup Dutch-processed cocoa \\
    & pinch salt \\
    \sfrac{3}{4} & cup light corn syrup \\
    1 & teaspoon vanilla extract \\
    8 & ounces milk chocolate, melted and cooled \\
}

Using a food processor, process butter, sugar, cocoa and salt until smooth. 
Add corn syrup and vanilla. 
Add chocolate and process until smooth.

\end{recipe}
