
\section{Baked Ziti}
\begin{recipe}

\pre{
    I usually make this with two dutch ovens, but you could also use a dutch oven and a sauté pan.
}

\ingredients{
    1 & pound rigatoni \\
}

Boil in salted water for five minutes less than the box directions. It will continue to cook in the oven.

\ingredients{
    28 & ounce tomato sauce \\
    14 & ounces diced tomatoes \\
     1 &  small onion \\
     5 &  cloves garlic \\
     3 &  tablespoons fresh basil \\
     2 &  teaspoons sugar \\
     1 &  teaspoon dried Oregano \\
}

Dice onions and sauté with olive oil in a small dutch oven until soft. Add minced garlic and cook until straw colored.

Add tomatoes, sauce, sugar and Oregano and simmer for 15 minutes. Stir in chiffonade basil and season with salt and pepper.

\ingredients{
    24 & ounces cottage cheese \\
     1 &  cup heavy cream \\
     1 &  cup grated Parmesan \\
     2 &  eggs \\
     1 &  tablespoon corn starch \\
     1 &  tablespoon hot sauce \\
}

Whisk cream and cornstarch in a dutch oven, and simmer over medium for two minutes.

Add cottage cheese, Parmesan, hot sauce and eggs, and mix with a wooden spoon. Add two cups of the tomato sauce and combine.

Add drained pasta, and toss to coat.

\columnbreak

\ingredients{
    1 & pound mozzarella \\
}

Cut mozzarella into \sfrac{1}{4} inch cubes, and add half to the pasta.

Cover the pasta with the remaining tomato sauce, and then the remaining mozzarella.

Bake for 30 minutes covered at 375\degree, then another 30 minutes uncovered. If it's not browned, put it under the broiler for 5 minutes.

Cool for 20 minutes, and serve.

\end{recipe}
